---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# seqstrclean

<!-- badges: start -->
<!-- badges: end -->

The goal of seqstrclean is to clean sequential strings.
In cumulative note taking, notes from a previous section may be saved alongside notes from the current section.
This package aims to remove the previous section's notes, leaving only notes from the current section.
For example, a person may take the note: "A cat ran up a tree." initially, then add "The cat was chased by a dog".
The notepad would then show: "A cat ran up a tree. The cat was chased by a dog".
This package is meant to separate the notes into the two parts based on the different saves of the notepad.

The firstnchar function compares the beginning of the latest notes to the previous section, and removes from the latest notes if they are similar enough (determined by edit distance).

The lcsclean function compares the entirety of both note sheets and locates the longest common substring between the two, which is removed from the latest note sheet if it represents a significant portion of the previous notes.

## Installation

You can install the development version of seqstrclean from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rachelesrogers/seqstrclean")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(seqstrclean)
## basic example code
```


