---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# seqstrclean

<!-- badges: start -->
<!-- badges: end -->

The goal of seqstrclean is to clean sequential strings.
In cumulative note taking, notes from a previous section may be saved alongside notes from the current section.
This package aims to remove the previous section's notes, leaving only notes from the current section.
For example, a person may take the note: "A cat ran up a tree." initially, then add "The cat was chased by a dog".
The notepad would then show: "A cat ran up a tree. The cat was chased by a dog".
This package is meant to separate the notes into the two parts based on the different saves of the notepad.

The firstnchar function compares the beginning of the latest notes to the previous section, and removes from the latest notes if they are similar enough (determined by edit distance).

The lcsclean function compares the entirety of both note sheets and locates the longest common substring between the two, which is removed from the latest note sheet if it represents a significant portion of the previous notes.

## Installation

You can install the development version of seqstrclean from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("rachelesrogers/seqstrclean")
```

## Example

There are three methods used for sequential note cleaning in this package: First N Character, Longest Common Substring, and a hybrid method combining the two. The First N Character method is faster, while in a small verification study the Longest Common Substring method was more accurate.
The hybrid method strikes a balance between the speed of the First N Character method and the accuracy of the Longest Common Substring method by only applying the Longest Common Substring method to difficult cases (where previous text cannot be removed using the First N Character method, or the supplied note sheet is unusually long).

### First N Character Method

The first method is the First N Character method, where the entirety of the previous page's notes are compared with the first n characters of the current page's notes (where n is the length of the previous page's notes). If the notes are similar enough (based on edit distance), the first n characters will be removed from the current page.

```{r fnc_example}
library(seqstrclean)

test_dataset <- data.frame(ID=c("1","1","2","2","1", "3", "3"),
Notes=c("The","The cat","The","The dog","The cat ran", "the chicken was chased", "The goat chased the chicken"),
Page=c(1,2,1,2,3,1,2))

test_dataset

```

In the test dataset shown above, there are third note-takes (identified by ID number), and 2-3 pages of notes.
The first individual wrote "The", "cat", and "ran" sequentially on their notes, with one word per page.
The second individual wrote "The" and "dog" sequentially.
The third individual wrote "the chicken was chased" on the first page, and "The goat chased the chicken" on the second page, which does not reflect sequential note-taking.
The First N Character method can be used to separate these notes, based on what was written per page.


```{r fnc_continued}

firstnchar(dataset=test_dataset,notes="Notes",char_diff=3,identifier="ID",pageid="Page")

```

Here, page_notes displays the clean notes, and edit_distance refers to the distance between the previous page of notes and the first n character of the current page of notes.
In the cases of sequential notes (for individuals 1 and 2), the edit distance is 0, as the beginning of the notes match the previous page's notes.
In the case of the third individual, the edit distance is 4 (there are four substitutions necessary to change from "goat" to "chick"), which is greater than the set threshold of 3.
Thus, the second page of the third individual's notes include the full text recorded on the second page (nothing was removed).

### Longest Common Substring Method

The second method is the Longest Common Substring method, where the two page note strings are compared in their entirity for the longest string they have in common, above a certain threshold.
This longest string is then removed from the current page of notes, and the process is repeated until the longest common substring is no longer above the assigned cutoff.

```{r lcs_example}
test_dataset <- data.frame(ID=c("1","1","2","2","1", "3", "3"),
Notes=c("The","The cat","The","The dog","The cat ran", "the chicken was chased", "The goat chased the chicken"),
Page=c(1,2,1,2,3,1,2))
```

The dataset above is the same as that of the First N Character method, aside from the third notetaker.
In this case, the third notetaker wrote "the chicken was chased" on the first page, and "The goat chased the chicken" on the second page.

```{r lcs_continued}
lcsclean(test_dataset,"Notes",0.5,"ID","Page")
```

When the proportion threshold is set to 0.5, nothing is removed from the third note taker's second page, as the longest common substring ("the chicken") represents exactly half of the characters in the page.

```{r lcs_continued_2}
lcsclean(test_dataset,"Notes",0.49,"ID","Page")
```

When the threshold is lowered to 0.49, "the chicken" is removed from the second page of notes.
This would represent the removal of the longest common substring after one iteration, as the next longest substring ("chased") does is below the cutoff threshold.

```{r lcs_continued_3}
lcsclean(test_dataset,"Notes",0.25,"ID","Page")
```

However, if the threshold is reduced further to 0.25 (or 1/4 of the previous notes), "chased" will be removed from the second page of notes as well, leaving only "the goat" in the clean notes.
